\documentclass[addpoints,12pt]{exam}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{multicol}
\usepackage{comment}
\usepackage{geometry}
\usepackage{enumitem}

\noprintanswers %Remove to hide answers
\pagestyle{headandfoot} %Adds Headers and Footers
\runningheadrule
\firstpageheader{Math 125}{Exam 2 }{\today}
\runningheader{Math 125}
{Exam 2, Page \thepage\ of \numpages}
{\today}
\firstpagefooter{}{\thepage}{}
\runningfooter{}{\thepage}{}

\newcommand{\tft}{
\begin{oneparcheckboxes}
\CorrectChoice True
\choice False
	\end{oneparcheckboxes}
}
\newcommand{\tff}{
\begin{oneparcheckboxes}
\choice True
\CorrectChoice False
	\end{oneparcheckboxes}
	
}
\newcommand{\ynn}{
\begin{oneparcheckboxes}
\choice Yes
\CorrectChoice No
	\end{oneparcheckboxes}
}
\newcommand{\yny}{
\begin{oneparcheckboxes}
\CorrectChoice Yes
\choice No 
	\end{oneparcheckboxes}
}
\checkboxchar{$\Box$}
\checkedchar{$\blacksquare$}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}

\newtheorem{lemma}{Lemma}
\begin{document}

%The box at the top, and the name
\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Answer the questions in the spaces provided on the
question sheets. If you run out of room for an answer,
continue on the back of the page.}}}
\end{center}
\vspace{0.1in}
\makebox[\textwidth]{Name:\enspace\hrulefill}
\vspace{0.2in}

%Question Formatting
%\qformat{\textbf{Question \thequestion}\quad (\thepoints)\hfill}
%Point Table

%\begin{center}
%\gradetable[h][questions]
%\end{center}

\begin{center}
    \Huge Formulas
\end{center}

\begin{lemma}
    The roots of a polynomial $y = ax^{2}+bx+c$ are given by 
		\[
		x = \frac{-b \pm \sqrt{b^{2}-4ac}}{2a}
		\]
\end{lemma}

\begin{lemma}
    If you would like to find a percent $r$ of a value $P$, you can use the formula 
		\[
		A = Pr
		\]
		If you would like to increase $P$ by a certain percent $r$, you can use 
		\[
		A = P(1+r)
		\]
\end{lemma}

\begin{lemma}
	The simple interest formula is given by 
    \[
    A = P(1+rt)
    \]
		The compound interest formula compounded yearly is given by 
		\[
		A = P(1+r)^{t} 
		\]
		The compound interest formula compounded $n$-times yearly is given by 
		\[
		A = P(1+\frac{r}{n})^{nt}
		\]
		Here $A$ is the amount of money you end with, $P$ is the starting value, $r$ is the rate , and $t$ is the number of years. 
		    
\end{lemma}
\begin{lemma}
    
\end{lemma}

\begin{center}
    \Huge Review Questions
\end{center}
%Beginning Questions
\begin{questions}
\question Consider the following list of sentences. Respond Yes if the sentence is a mathematical statement, and No if it is not. 
\begin{enumerate}[label = \alph*)]
	\item \yny The earth is the third planet from the sun.   
	\item \ynn Do your homework. 
	\item \ynn What time does the exam start? 
	\item \yny The ocean does not contain salt water. 
	\item \ynn The Minnesota Vikings are the best football team.  
\end{enumerate}
\question Consider the following statements 
\begin{align*}
	p:  & \text{The dog's name  is Nels.} \\
	q: & \text{Nels has a new toy. } \\
	r: & \text{Nels is at the dog park.} \\
\end{align*}
Write the statement expressed by the symbolic statement in words. 
\begin{enumerate}[label = \alph*)]
    \item $p $ 
		\item $q \wedge r$ 
		\item $\sim r $
		\item $q \leftrightarrow  r $ 
		\item  $q \vee r $
\end{enumerate}
\question Write the negation of the following statements 
\begin{enumerate}[label = \alph*)]
	\item All people in the class received an $A$ on the exam. 
	\item It is not Monday. 
	\item There exists a jellybean in the candy jar. 
	\item We all live in Yankton. 
	\item Some cats do not like to swim. 
\end{enumerate}
\question Solve the following linear equation 
\[
2(x-3)-2 = 3-3(x+2) 
\]
\question The formula 
\[
C = \frac{5}{9}(F-32)
\]
expresses the relationship between Farenheit temperature, $F$, and Celsius temperate $C$. Evaluate the expression at $F = 41$ to find the equivalent temperature at the Celsius scale. 
\question Solve the quadratic equation by factoring 
\[
x^{2}-2x-15 = 0 
\]
\question Solve the following quadratic equation using the quadratic formula. 
\[
x^{2}+5x - 4 = 0 
\]
Do \textbf{NOT} simplify the quadratic formula after applying the quadratic formula. 
\question Solve and give the solution set by indicating on a number line. 
\[
-4x + 7 \geq -5 
\]
\question  You are considering buying a Traeger Grill for your parents for Christmas. The Pro 780 model costs $999.95$ at Ace Hardware. The sales tax at Ace Hardware in Yankton is $6.2\%$. 
\begin{enumerate}[label = \alph*)]
	\item How much sales tax do you pay in total on your purchase? 
	\item What is the total cost of the grill? 
\end{enumerate}
\question You are looking to invest $2000$ dollars. A bank gives you two options. You can either invest into an account that gives simple interest at $10\%$ per year, or you can invest in an account that makes $8\% $ compound interest. 
\begin{enumerate}[label = \alph*)]
	\item After $4$ years, which account is the better investment? 
	\item After $8$ years, which account is the better investment? 
	\item Which account will be the better investment in the short term? Why is this? 
	\item Which account will be the better investment in the long run? Why is this? 
\end{enumerate}
    \question Assume that you buy a new car that costs $\$25000$ dollars. You finance it with a $3$ year loan at $4\%$. Assume you make monthly payments. What is the monthly payment for your car loan?
\end{questions}

    
\end{document}
